---
title: "salad package"
subtitle: 'Version 1.0'
author: "Hervé Perdry"
version: 0.1
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{milorGWAS package}
  %\VignetteDepends{milorGWAS}
  %\VignettePackage{milorGWAS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r echo = FALSE}
oldoptions <- options()
oldpar <- par()
options(width = 120)
require(salad)
```

<style type="text/css">
h1.title {
  font-size: 200%;
}

h1 {
  font-size: 160%;
}

h2 {
  font-size: 130%;
}

pre {
  padding: 0px;
  margin: 0 0 0.5em 0;
}

div.sourceCode {
  margin: 0px;
}

</style>

# Introduction

Salad is a package for Automatic Differentiation. Its name could stand for Simple And
Light Automatic Differentiation, but it stands well by itself (eat salad, salad is good).

Lots of efforts have been done to allow re-using code written without automatic differentiation 
in mind. Consider for example the following function (which does nothing very interesting, 
except using `ifelse`, `cbind`, and some matrix arithmetic) :

```{r}
f <- function(x) {
  a <- x**(1:2)
  b <- ifelse(a > 1, sin(a), 1 - a) 
  C <- crossprod( cbind(a,b) )
  det(C)
}
```

The value of its derivative for a given `x` is easy to obtain with salad.

```
# value of f in x = 0.2
f(0.2)
# creating a dual number for x = 0.2
x <- dual(0.2)
y <- f(x)
y
# and now the derivative 
d(f(y))
```

